On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-01 MS.tex
Change the results part to include a clear comparison of RGR vs AGR Re-read and modify slightly the abstract and the discussion to include the new results.

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[]{natbib}

@@

\item Results were consistent with predictions, although there were some limitations arising from unequal numbers of observation across ontogenetic stages. Specific leaf area was correlated with relative growth rate in seedlings but not in adult plants. Correlations of growth with wood density and assimilation rate were not affected by ontogenetic stage. Seed mass and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings and adults, respectively.

@@

\subsubsection*{Measurements under ``ideal'' conditions}\label{ideal-vs-entire-dataset}

The entire dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses. Consequently, we adopted a two-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across strudies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). This dataset is called the ``ideal'' dataset. We then compared the results from the ``ideal'' dataset with those from the entire dataset - with both relative growth rate and absolute growth rates, and all other criteria relaxed.

@@

\subsection*{Main effects for relative growth rate under ``ideal'' conditions}

We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species. Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.

@@

We now report results for relative growth rate from the entire dataset. Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication. This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig. \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

Results from the entire dataset reinforced our conclusions for both SLA and wood density and allowed us to compare correlations with growth across ontogenetic stages for Aarea and seed mass. For SLA and wood density, although the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ``ideal'' subset (Fig. \ref{fig:fig4})). As expected for seed mass, the correlation with growth at adult stage was significantly different from that observed at seedling stage (see CIs in Fig. \ref{fig:fig4}c, and model fit improved when stage was incorporated). For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across ontogenetic stage. The results were consistent with the prediction for a positive correlation with relative growth rate across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero). Comparison of Aarea effect between the ``ideal'' subset (Fig. \ref{fig:fig3}d) and entire dataset (Fig. \ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added. For maximum height, there were still too few replicates to conclude undoubtedly that the correlation is absent for smaller sizes.

\subsection*{Comparisons of relative and absolute growth rates under relaxed criteria}

For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available. Indeed for SLA
For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate. Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large. While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies. Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations. Growth rates were already known to change with size \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory. Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases. This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.

@@

For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model. This suggests the mechanisms through which traits affect growth are correctly represented in the model. For SLA the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation. For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.

@@

For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5). In our model, cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
For seedlings a negative correlation arose regardless of whether wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e. stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.

As far as we are aware, our study is the first to compare Aarea and growth correlations between small and large plants. In the growth model, a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate. Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=3). In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.

Meta-analysis showed a positive correlation between maximum height and relative growth rate for adult stage, but not for saplings and seedlings. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, maximum height was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the maximum height-relative growth rate relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. A possible mechanism  for Poorter et al's observation is captured by our growth equations: maximum height affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their maximum height are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates. While the results of the meta-analysis were consistent with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1). Consequently, subsequent research is welcomed to validate this result.

@@

Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, (3) expressing plant sizes on continuous scales of mass or height, rather than through the approximate and partly subjective categories unavoidably adopted here, and (4) moving beyond the qualitative model predictions evaluated here towards quantitative predictions, e.g. via the recently published \texttt{plant} model \citep{Falster-2016}. Additional data are specifically required in small plants (seedling and sapling) for wood density and maximum height, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g. LMR, LAR). However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth. Thus, the linkage of growth to the mechanisms outlined here can shed light on tree growth trajectories and the size-dependent effects of functional traits on the changing species growth rate rankings as individuals grow larger.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{ The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means adding a stage effect to the model significantly improved model fit. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage. The legend is identical to Fig 3, with two exceptions. i) Results shown are from the entire dataset (see methods for details). ii) Likelihood Ratio Tests were calculated on effect size combining relative growth rate and absolute growth rate exclusively.}
\label{fig:fig4}
\end{figure}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[]{natbib}
\usepackage{floatpag}
\floatpagestyle{empty}

@@

\item Results were consistent with predictions, although there were some limitations arising from unequal numbers of observation across ontogenetic stages. Specific leaf area was correlated with relative growth rate in seedlings but not in adult plants. Correlations of growth with wood density were not affected by ontogenetic stage. Seed mass, assimilation rate and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings, seedlings and adults, respectively.

@@

\subsubsection*{Analyses of relative and absolute growth rates under conservative and relaxed criteria}\label{conservative-vs-entire-dataset}

The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses. Consequently, we adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). We then compared these results with those focusing on relative growth rate from the entire dataset - with all criteria relaxed excepted the growth measurement used. Finally, we compared results from both relative and absolute growth rates from the entire dataset.

@@

\subsection*{Main effect for relative growth rates under conservative criteria}

We identified only 55 studies containing 137 correlations reporting data measured under conservative criteria: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species. Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.

@@

We now report results for relative growth rate from the entire dataset. Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication. This entire dataset included correlations measured with relative growth rate exclusively (Fig. \ref{fig:fig3}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e. traits could be measured on a different ontogenetic stage to growth data) or environmental conditions. The relaxed criteria increased the number of replicates, from $n = 137$ to $n = 167$ correlations across 93 articles. However, the additional replicates were unequally distributed across trait-stage combinations. Some trait-stage combinations that already had a lot of data got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates. On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.

Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not altered them for the others traits. For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig. \ref{fig:fig3})). For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e). Comparison of Aarea effect between the conservative and relaxed criteria (Fig. \ref{fig:fig3}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added. For maximum height, there were no additional replicates in the entire dataset; we still cannot conclude undoubtedly that the correlation is absent for smaller sizes.

\subsection*{Comparisons between relative and absolute growth rates under relaxed criteria}

We had hypothesized only for seed mass that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate. Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with either abolute or relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate change as plants grow from small to large. While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies. Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations. Growth rates were already known to change with size \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory. Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases. This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.

@@

For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model, although there were some limitations arising from unequal numbers of observation across ontogenetic stages. This suggests the mechanisms through which traits affect growth are correctly represented in the model. For SLA the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation. For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.

@@

For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=1-4). In our model, cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
For seedlings a negative correlation arose regardless of whether wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e. stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.

As far as we are aware, our study is the first to compare Aarea and growth correlations between small and large plants. In the growth model, a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate. Meta-analyses showed a positive correlation for seedling but not for saplings and adult (n=1). In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.

Meta-analysis showed a positive correlation between maximum height and relative growth rate for adult stage. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, maximum height was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the maximum height-relative growth rate relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. A possible mechanism for Poorter et al's observation is captured by our growth equations: maximum height affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their maximum height are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates. While the results of the meta-analysis not countered with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1). Consequently, subsequent research is welcomed to demonstrate this result on small plant sizes.

@@

Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, (3) expressing plant sizes on continuous scales of mass or height, rather than through the approximate and partly subjective categories unavoidably adopted here, and (4) moving beyond the qualitative model predictions evaluated here towards quantitative predictions, e.g. via the recently published \texttt{plant} model \citep{Falster-2016}. Additional data are specifically required in small plants (seedling and sapling) for wood density and maximum height, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g. LMR, LAR). However, the existing published evidence is consistent with several qualitative predictions of a simple model that assesses the effects of plant size on growth. Thus, the linkage of growth to the mechanisms outlined here can shed light on tree growth trajectories and the size-dependent effects of functional traits on the changing species growth rate rankings as individuals grow larger.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Results shown are for the "conservative dataset" (i.e. correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same) and for the entire dataset (i.e. with all criteria relaxed, see methods for details). Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset. A significant p-value means adding a stage effect to the model significantly improved model fit.}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage. The legend is identical to Fig 3, with two exceptions. i) Results shown are from the entire dataset (see methods for details). ii) Likelihood Ratio Tests compared maximum-likelihood fits between a model separated by stage and one separared by stage and growth measurement (RGR vs AGR).}
\label{fig:fig4}
\end{figure}

### 2016-03-01 ms-suppinfo.tex
LIzzy comments 1
Change the results part to include a clear comparison of RGR vs AGR Re-read and modify slightly the abstract and the discussion to include the new results.

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. The smaller the AIC, the better the model is. Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study. In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if CIs do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data , grey points: all the data (for details see ``Material and Methods''). ``n'' indicates the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

@@

\noindent\textbf{Results:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig. \ref{fig:figA7}). Funnel plots exhibited a typical funnel shape for all five functional traits analysed, showing no evidence for publication bias (Fig. \ref{fig:figA7}).
The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "ideal" dataset). In the entire dataset, the estimated number of missing value ranges from 0 to 11 depending on the trait considered (Fig. \ref{fig:figA7}). The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$ to 0.48 $\pm$ 0.07 for SLA and from $-0.48 \pm 0.11$ to \ensuremath{-0.29}$\pm$ 0.12 for the seed mass, suggesting a lower correlation coefficient for SLA, and a higher for seed mass. Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant (CIs not overlapping zero; SLA CI 0.35 to 0.62, Seed mass CI \ensuremath{-0.51} to \ensuremath{-0.06}).

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. The smaller the AIC, the better the model is. Results shown here are from ``conservative'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``conservative'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the ``conservative'' subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "conservative" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study. In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if CIs do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: conservative data , grey points: all the data (for details see ``Material and Methods''). ``n'' indicates the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

@@

\noindent\textbf{Results:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig. \ref{fig:figA7}). Funnel plots exhibited a typical funnel shape for all five functional traits analysed, showing no evidence for publication bias (Fig. \ref{fig:figA7}).
The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "conservative" dataset). In the entire dataset, the estimated number of missing value ranges from 0 to 11 depending on the trait considered (Fig. \ref{fig:figA7}). The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$ to 0.48 $\pm$ 0.07 for SLA and from $-0.48 \pm 0.11$ to \ensuremath{-0.29}$\pm$ 0.12 for the seed mass, suggesting a lower correlation coefficient for SLA, and a higher for seed mass. Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant (CIs not overlapping zero; SLA CI 0.35 to 0.62, Seed mass CI \ensuremath{-0.51} to \ensuremath{-0.06}).
